\documentclass{article}

\usepackage{xeCJK}
\setCJKmainfont{SimSun}

\title{FPGA Homework IV}
\author{李约瀚 \\ 14130140331 \\ qinka@live.com \\ me@qinka.pro \\ qinka@qinka.pw(remove soon)}

\usepackage{listings}
\usepackage{hyperref}

\begin{document}
    \maketitle
    \newpage
    \tableofcontents
    \newpage
    \section{Summary}
    \label{sec:summary}
    
    In this homework, I try to describe a one-bit comparator in VHDL.
    I use both of \lstinline[language=VHDL]|xor| and with-select notation to represent a comparator. 
    The delay of the one with with-select notation is short than ones which is using \lstinline[language=VHDL]|xor|.
    When the frequency of the input signals  are higher then 50MHz,
    the delay of the one, which is using \lstinline[language=VHDL]|xor|, can not be ignored,
    and it has effects on other signals. However, The one with with-select notation is well.

    There are also the behaviorl simulation and the post-route simulation of the comparator.
    And there is also RTL schematics.


    \section{Represent}
    \label{sec:represent}

    For such a comparator, it will return a ``true'' signal, in logic, when the two input signals are same, in logic.
    So it is smae with ``xor''. Then the first idear of the comparator is using ``xor''. And then we can also use with-select notation.
    And the following codes is the sources of comparator.

    Firstly, we need using the libraries from IEEE.

\begin{lstlisting}[language=VHDL]
library IEEE;
use IEEE.STD_LOGIC_1164.ALL;
\end{lstlisting}

    Then I need to define the comparator.

\begin{lstlisting}[language=VHDL]
entity comparator is
  port( A : in  STD_LOGIC
      ; B : in  STD_LOGIC
      ; C : out STD_LOGIC
      );
ebd comparator;
\end{lstlisting}

    Then I represent the comparator with ``xor''.

\begin{lstlisting}[language=VHDL]
architecture xor_one of comparator is
begin
  C <= A xor B;
end xor_one;
\end{lstlisting}
    
    Then it is the one using with-select notation.

\begin{lstlisting}[language=VHDL]
architecture with_one of comparator is
  signal I : STD_LOGIC_VECTOR(1 downto 0);
begin
  with I select
  C <= '1' when '11',
       '1' when '00',
       '0' when others;
  I(0) <= A;
  I(1) <= B;
end with_one;
\end{lstlisting}


    \section{Behavioral Simulation}
    \label{sec:behavioralsimulation}

    Here I need to simulate the two of the comparator, so I write one test bench with the both of the kinds of comparator.

\begin{lstlisting}[language=VHDL]
library IEEE;
use IEEE.STD_LOGIC_1164.ALL;
 
ENTITY tb_comparator IS
END tb_comparator;
\end{lstlisting}

    \textit{in this ``architecture''}
\begin{lstlisting}[language=VHDL]
ARCHITECTURE behavior OF tb_comparator IS 
\end{lstlisting}
    
    To test this comparator, firstly, we need to write down the component declaration for the unit under test.

\begin{lstlisting}[language=VHDL]
  component comparator
  port( A :  IN std_logic
      ; B :  IN std_logic
      ; C : OUT std_logic
      );
  END COMPONENT;
\end{lstlisting}

    The I define the signals used in this architecture. 

\begin{lstlisting}[language=VHDL]
  signal A : std_logic := '0';
  signal B : std_logic := '0';
  signal C : std_logic_vector(1 downto 0) := "00";
\end{lstlisting}

    Also, I define the period of the clock which control the input signals' frequency.

\begin{lstlisting}[language=VHDL]
  constant clock_period : time := 20 ns;
\end{lstlisting}

   Instantiate the unit under test

\begin{lstlisting}[language=VHDL]
BEGIN
  uut_xor: comparator PORT MAP (
          A => A,
          B => B,
          C => C(0)
        );
  uut_with: comparator PORT MAP (
          A => A,
          B => B,
          C => C(1)
        );
\end{lstlisting}
    
\end{document}